Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-04-27 main.Rmd
put all discussion on implementation in the data structures section.

```{r linear-time, echo=FALSE, out.width = "100%", fig.cap="The time domain distributed as linear granularities hour, day, week, month and year. These are ordered with ordering guided by integers and hence is unidirectional and non-repeating."}
knitr::include_graphics("Figs/linear-arr3.png")
```

@@

Cyclic granularities represeent cyclical components in time.  Weeks is an example of a cyclical granularity because every 7 days there's another Monday. Cyclic granularities can be constructed by conducting modular arithmetic on two linear granularities. Cycles can be either _regular_, called **circular**, or _irregular_, **quasi-circular**. <!-- with every granule of coarser linear granularity being made up of same (regular) or different (irregular) number of granules of finer linear granularity. For example, a regular mapping exists between  (where 60 minutes always add up to 1 hour), while an irregular mapping exists between  (as the number of days per month ranges from 28 to 31). A grouping operation in Calendar algebra could lead to a regular mapping, whereas a altering-tick operation could result in an irregular mapping. Cyclic time granularities are referred to as **circular** if mappings are regular and **quasi-circular** if the mappings are irregular. Examples of common circular granularities include hour of the day and day of the week, whereas examples for quasi-circular granularities are day of the month and week of the month.-->

@@

Cyclic time granularities can be implemented through the tsibble [@wang2019tsibble] (Time Series taBBLE) data structure. A tsibble consists of an index, key and measured variables. An index is a variable with inherent ordering from past to present and a key is a set of variables that define observational units over time. <!--In a tsibble, each observation (row) is uniquely identified by index and key.--> A time domain, as defined by @Bettini1998-ed, is essentially a mapping of the index set to the index of a tsibble. A linear granularity is a mapping of the index set to subsets of the time domain. For example, if the index of a tsibble is days, then a linear granularity might be weeks, months or years. A bottom granularity is represented by the index of the tsibble.<!--Consistent with the assumption of @Bettini2000-vy, all linear granularities can be generated from the bottom granularity by calendar algebraic operations.-->\todo[inline]{Would it be worth to start this discussion about data structures earlier, with the linear granularity, and follow it through when appropriate; or put all discussion on implementation in the data structures section.}

@@

```{r circular-dow,echo=FALSE,out.width = "100%",fig.cap="Illustration of circular relative to linear granularities (a). Circular granularities can be considered to be cutting the linear granularity into pieces and stacking them (b). The circular granularity creates repeated integer sequences."}
knitr::include_graphics("Figs/circularex.png")
```

@@

knitr::include_graphics("Figs/quasiex.png")

@@

The cyclic calendar algebra consists of broadly two kinds of operations:
(1) **single-to-multiple** and (2) **multiple-to-single** which entails the representation of _multiple-order-up_ cyclic granularities from _single-order-up_ cyclic granularities and vice versa. The hierarchical structure of time creates a natural nested ordering which can produce single-order-up or multiple-order-up granularities. We shall use the notion of a hierarchy table and order to define them.

**Order** of a linear granularity can be comprehended as the level of coarseness associated with a linear granularity. For example, for two linear granularities $G$ and $H$, if $G$ groups into or finer than $H$ or $H$ is composed of higher number of granules of the bottom granularity than $G$, then $G$ is of lower order than $H$. In any hierarchy table, linear granularities are arranged from lowest to highest order.

@@

We consider the case of only one quasi-circular single order-up granularity in the hierarchy table. Any multiple-order-up quasi-circular granularity $C_{l, m}(z)$ can then be obtained as a function of a single (or multiple) order-up circular granularity $C_{l,m'}(z)$ and single order-up quasi-circular granularity $C_{m',m}(z)$ or vice versa. Two different approaches need to be employed leading to the following cases:

@@

Effective exploration and visualization require proper data structures. It is recognized that there is a crucial influence of linear vs cyclic time characteristics on the expressiveness of visualization and analysis. Moreover, one can use calendars based on application domain that define contextual system of linear and cyclic granularities. A recent tidy data structure to support exploration and modeling of temporal data is tsibble [@wang2019tsibble], where data is structured in a semantic manner with reference to observations and variables, with the time index stated explicitly. Since all cyclic granularities can be expressed in terms of the index set, we consider the data structure in Figure \@ref(fig:data-structure) for exploration of temporal data of this kind. This is a two-dimensional array extending the columns of tsibble by including the cyclic granularities $C_i$ and $v$ denotes the measurement variable. The total number of cyclic granularities would be based on the number of linear granularities considered in the hierarchy table and presence of any aperiodic cyclic granularities. Suppose we have $n$ linear granularities in the hierarchy table, $n(n-1)/2$ circular or quasi-circular cyclic granularities could be constructed. Any attempt to encode all or many cyclic granularities at the same time to develop insights on periodicity might fail or otherwise become too numerous for comprehensive human consumption. Instead, this big problem is broken down by focusing on two cyclic granularities at a time. Hence data sets of the form <$C_i$, $C_j$, $v$> forms the basis for exploration and analysis of the measured variable.

@@

\begin{definition}\label{def:clash}
A {\bf harmony} is a pair of cyclic granularities that does not contain any missing combinations of its categories.
\end{definition}

@@

scene1 <-  VIC %>%
  #create_gran("quarter_year") %>%
  #filter(month_year %in% c("Jan", "Mar", "Dec")) %>%
  #create_gran("day_week") %>%
  #filter(day_week %in% c("Sat", "Sun", "Mon")) %>%
  prob_plot("quarter_year", "wknd_wday",
            response = "general_supply_kwh",
            plot_type = "lv",
            symmetric = FALSE
  ) +
  ylab("") +
  #xlab("weekend/weekday") +
  scale_fill_brewer(palette = "Dark2") + theme(legend.position = "right") + ggtitle("") + scale_y_log10() + xlab("")

scene2 <- VIC %>%
  #create_gran("month_year") %>%
  #filter(month_year %in% c("Jan", "Mar", "Dec")) %>%
  #create_gran("day_week") %>%
  #filter(day_week %in% c("Sat", "Sun", "Mon")) %>%
  prob_plot("wknd_wday",
            "quarter_year",
            response = "general_supply_kwh",
            plot_type = "lv",
            symmetric = FALSE
  ) +
  ylab("") +
    xlab("quarters of the year")  +
  scale_fill_brewer(palette = "Paired") + theme(legend.position = "right") + ggtitle("") + scale_y_log10()

@@

scene3 <- VIC %>%
  #create_gran("month_year") %>%
  #filter(month_year %in% c("Jan", "Mar", "Dec")) %>%
  #create_gran("day_week") %>%
  #filter(day_week %in% c("Sat", "Sun", "Mon")) %>%
  prob_plot("quarter_year",
            "month_year",
            response = "general_supply_kwh",
            plot_type = "lv",
            symmetric = FALSE
  ) +
  ylab("") +
  xlab("months of the year") + theme(legend.position = "right") + scale_fill_brewer(palette = "Set2") + ggtitle("") + scale_y_log10()

@@

ggpubr::annotate_figure(gg_fig,
                left = text_grob("electricity demand [KWh]",  rot = 90))

@@

# plot for only customer is shown
# cust1 <- smart_meter10 %>%
# filter(customer_id %in% c(10006704)) %>%
#   prob_plot("wknd_wday",
#                             "hour_day",
#                             response = "general_supply_kwh",
#                             plot_type = "quantile",
#             symmetric = FALSE,
#             quantile_prob = c(0.25, 0.5, 0.75, 0.9))
#   scale_y_sqrt() +
#   ggtitle("Energy consumption distribution for customer id: 10006704")
cust2_quantile <- smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>%
  prob_plot("wknd_wday",
    "hour_day",
    response = "general_supply_kwh",
    plot_type = "quantile",
    symmetric = TRUE,
    quantile_prob = c(0.01, 0.1, 0.25, 0.5, 0.75, 0.9, 0.99)
  ) +
  scale_y_sqrt() +
  #ggtitle(" (b) Area quantile plot faceted by weekend-weekday") +
  ylab("electricity demand [KWh]") + xlab("hours of the day") + ggtitle("") + ylab("")
#
# smart_meter10 %>%
#   filter(customer_id %in% c(10006704)) %>%
#   prob_plot("wknd_wday",
#                             "hour_day",
#                             response = "general_supply_kwh",
#                             plot_type = "violin") +
#   scale_y_sqrt() +
#   ggtitle("Energy consumption distribution for customer id: 10006704")

cust2_violin <- smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>%
  prob_plot("wknd_wday",
    "hour_day",
    response = "general_supply_kwh",
    plot_type = "violin"
  ) +
  scale_y_sqrt()+
  #ggtitle(" (c) Violin plot faceted by weekend-weekday") +
  ylab("") + xlab("hours of the day") + ggtitle("") +
  scale_x_discrete( breaks = seq(0, 23, 5))

cust2_box <- smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>%
  prob_plot("hour_day",
    "wknd_wday",
    response = "general_supply_kwh",
    plot_type = "boxplot"
  ) +
  scale_y_sqrt() +
  #ggtitle(" (a) Box plot faceted by hour-of-day") +
  xlab("") +
  ggtitle("") + ylab("") +
  scale_x_discrete(labels = c('wday','wend')) +
  ggplot2::theme(axis.text.x = element_text(size = 7))

@@

First, it would be interesting to see if the distribution of total runs vary depending on if a team bats in the first or second inning. The Mumbai Indians (MI) and Chennai Super kings (CSK) <!--are considered one of the best teams in IPL with multiple winning titles and --> appeared in final playoffs from 2010 to 2015. We take their example in order to dive deeper into this question. <!--Circular granularities "over-of-inning" and "inning-of-match" can be computed using \ref{sec:circular-gran-def} with over as index of the tsibble.--> From Figure \ref{fig:cricex}(a), it can be observed that for the team batting in the first inning there is an upward trend of runs per over, while there is no clear upward trend in median and quartile deviation of runs for the teams batting in the second inning. This seem indicate that players feel mounting presure to score more runs as they approach towards the end of the first inning. Whereas teams batting in the second inning have a set target in mind and are not subjected to such mounting press and may adopt a more conservative strategy, to score runs. Thus winning teams like CSK and MI seem to emply different inning strategies when it comes to their batting order.

@@

Another interesting question could is: do runs per over decrease in the subsequent over if fielding (defending) was good in the previous over? For establishing that the fielding quality, we apply an indicator function on dismissals (1 if there was at least one catch in the previous over, 0 otherwise). Runs in the current over is then the observation variable.  <!--If a batsman is bowled out, it does not necessarily signify good fielding. So we only include number of catches and run out in an over as a measure of good fielding.
Difference in runs across overs are likely to be negative if good fielding has an impact on the runs scored in the subsequent overs. --> Dismissals in the previous over can lead to a batsman adopting a more defensive play style. Figure \ref{fig:cricex}(b) shows that when there are no dismissals in the previous over, leads to a higher median and quartile spread of run rate per over as compared to the case when there has been at least one dismissal in the previous over.

@@

cricket_tsibble %>%
  filter(batting_team %in% c(
    "Mumbai Indians",
    "Chennai Super Kings"
  )) %>%
  mutate(inning = paste0("innings: ", inning)) %>%
  prob_plot("inning",
    "over",
    response = "runs_per_over",
    hierarchy_model,
    plot_type = "lv"
  ) +
  scale_fill_brewer(palette = "Dark2") +
  #ggtitle("(a) Runs per over across over faceted by inning") +
  theme(legend.position = "right") +
  ggtitle("a") +
  ylab("runs per over") +
  xlab("overs of the innings") +
  theme(plot.title = element_text(face = "bold")) +
  ggplot2::theme(
       strip.text = ggplot2::element_text(
        size = 10,
         margin = ggplot2::margin(b=0, t=0)
      )
     )

@@

# filter(fielding_wckts %in% c(0,1)) %>%
#
 cricket_data %>%
  filter(over!=1) %>%
  prob_plot("over", "lag_field",
  hierarchy_model,
  response = "run_rate",
  plot_type = "boxplot",
  symmetric = FALSE,
 quantile_prob = c(0.25, 0.5, 0.75)) +
   #ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") +
  ylab("runs per over")  +
  xlab("number of wickets in previous over") +
  ggtitle("b") +
   theme(plot.title = element_text(face = "bold"))
# + geom_boxplot(width = 0.5, aes(colour = lag_field))
```

>>>>

```{r linear-time, echo=FALSE, out.width = "100%", fig.cap="The time domain distributed as linear granularities hour, day, week, month and year. These are ordered with ordering guided by integers and hence is unidirectional and non-repeating."}
knitr::include_graphics("Figs/linear-ex.png")
```

@@

\todo[inline]{Check with Di to revise the first two statements}
Cyclic granularities represent cyclical repetitions in time. Weeks is an example of a cyclical granularity because every 7 days there's another Monday. Cyclic granularities can be constructed by conducting modular arithmetic on two linear granularities. Cycles can be either _regular_, called **circular**, or _irregular_, **quasi-circular**. <!-- with every granule of coarser linear granularity being made up of same (regular) or different (irregular) number of granules of finer linear granularity. For example, a regular mapping exists between  (where 60 minutes always add up to 1 hour), while an irregular mapping exists between  (as the number of days per month ranges from 28 to 31). A grouping operation in Calendar algebra could lead to a regular mapping, whereas a altering-tick operation could result in an irregular mapping. Cyclic time granularities are referred to as **circular** if mappings are regular and **quasi-circular** if the mappings are irregular. Examples of common circular granularities include hour of the day and day of the week, whereas examples for quasi-circular granularities are day of the month and week of the month.-->

@@

@@

```{r circular-dow,echo=FALSE,out.width = "100%",fig.cap="Illustration of circular relative to linear granularities (a). Circular granularities can be considered to be cutting the linear granularity into pieces and stacking them (b). The circular granularity creates repeated integer sequences."}
knitr::include_graphics("Figs/circular-ex.png")
```

@@

knitr::include_graphics("Figs/quasi-ex.png")

@@

The cyclic calendar algebra consists of broadly two kinds of operations:
(1) **single-to-multiple** and (2) **multiple-to-single** which entails the representation of _multiple-order-up_ cyclic granularities from _single-order-up_ cyclic granularities respectively. The hierarchical structure of time creates a natural nested ordering which can produce single-order-up or multiple-order-up granularities. We shall use the notion of a hierarchy table and order to define them.

**Order** of a linear granularity can be comprehended as the level of coarseness associated with a linear granularity. For example, for two linear granularities $G$ and $H$, if $G$ _groups into_ or _finer than_ $H$ or $H$ is composed of higher number of granules of the bottom granularity than $G$, then $G$ is of lower order than $H$. In any hierarchy table, linear granularities are arranged from lowest to highest order.

@@

We consider the case of only one quasi-circular single order-up granularity in the hierarchy table. Any multiple-order-up quasi-circular granularity $C_{l, m}(z)$ can then be obtained as a
dicrete combination of circular and quasi-circular granularities.
<!--function of a single (or multiple) order-up circular granularity $C_{l,m'}(z)$ and single order-up quasi-circular granularity $C_{m',m}(z)$ or vice versa. --> Depending on the order of combination, two different approaches need to be employed leading to the following cases:

@@

Effective exploration and visualization require proper data structures. It is recognized that there is a crucial influence of linear vs cyclic time characteristics on the expressiveness of visualization and analysis. Moreover, one can use calendars based on application domain that define contextual system of linear and cyclic granularities. A recent tidy data structure to support exploration and modeling of temporal data is tsibble [@wang2019tsibble] (Time Series taBBLE) data structure. A tsibble consists of an index, key and measured variables. An index is a variable with inherent ordering from past to present and a key is a set of variables that define observational units over time. A linear granularity is a mapping of the index set to subsets of the time domain. For example, if the index of a tsibble is days, then a linear granularity might be weeks, months or years. A bottom granularity is represented by the index of the tsibble. Since all cyclic granularities can be expressed in terms of the index set, we consider the data structure in Figure \@ref(fig:data-structure) for exploration of temporal data of this kind. This is a two-dimensional array extending the columns of tsibble by including the cyclic granularities $C_i$ and $v$ denotes the measurement variable. The total number of cyclic granularities would be based on the number of linear granularities considered in the hierarchy table and presence of any aperiodic cyclic granularities. Suppose we have $n$ linear granularities in the hierarchy table, $n(n-1)/2$ circular or quasi-circular cyclic granularities could be constructed. Any attempt to encode all or many cyclic granularities at the same time to develop insights on periodicity might fail or otherwise become too numerous for comprehensive human consumption. Instead, this big problem is broken down by focusing on two cyclic granularities at a time. Hence data sets of the form <$C_i$, $C_j$, $v$> forms the basis for exploration and analysis of the measured variable.

<!-- CONTENT SHORT -->
<!-- Cyclic time granularities can be implemented through the tsibble [@wang2019tsibble] (Time Series taBBLE) data structure. A tsibble consists of an index, key and measured variables. An index is a variable with inherent ordering from past to present and a key is a set of variables that define observational units over time. <!--In a tsibble, each observation (row) is uniquely identified by index and key.A time domain, as defined by @Bettini1998-ed, is essentially a mapping of the index set to the index of a tsibble. A linear granularity is a mapping of the index set to subsets of the time domain. For example, if the index of a tsibble is days, then a linear granularity might be weeks, months or years. A bottom granularity is represented by the index of the tsibble.<!--Consistent with the assumption of @Bettini2000-vy, all linear granularities can be generated from the bottom granularity by calendar algebraic operations.\todo[inline]{Would it be worth to start this discussion about data structures earlier, with the linear granularity, and follow it through when appropriate; or put all discussion on implementation in the data structures section.} -->

@@

\begin{definition}\label{def:clash}
A {\bf harmony} is a pair of cyclic granularities that does not contain any empty combinations of its categories.
\end{definition}

@@

scene1 <-  VIC %>%
  #create_gran("quarter_year") %>%
  #filter(month_year %in% c("Jan", "Mar", "Dec")) %>%
  #create_gran("day_week") %>%
  #filter(day_week %in% c("Sat", "Sun", "Mon")) %>%
  prob_plot("quarter_year", "wknd_wday",
            response = "general_supply_kwh",
            plot_type = "lv",
            symmetric = FALSE
  ) +
  ylab("") +
  #xlab("weekend/weekday") +
  scale_fill_brewer(palette = "Dark2") + theme(legend.position = "right") + ggtitle("") + scale_y_log10() + xlab("")+ 
  theme_minimal()

scene2 <- VIC %>%
  #create_gran("month_year") %>%
  #filter(month_year %in% c("Jan", "Mar", "Dec")) %>%
  #create_gran("day_week") %>%
  #filter(day_week %in% c("Sat", "Sun", "Mon")) %>%
  prob_plot("wknd_wday",
            "quarter_year",
            response = "general_supply_kwh",
            plot_type = "lv",
            symmetric = FALSE
  ) +
  ylab("") +
    xlab("quarters of the year")  +
  scale_fill_brewer(palette = "Paired") + theme(legend.position = "right") + ggtitle("") + scale_y_log10() + theme_minimal()

@@

scene3 <- VIC %>%
  #create_gran("month_year") %>%
  #filter(month_year %in% c("Jan", "Mar", "Dec")) %>%
  #create_gran("day_week") %>%
  #filter(day_week %in% c("Sat", "Sun", "Mon")) %>%
  prob_plot("quarter_year",
            "month_year",
            response = "general_supply_kwh",
            plot_type = "lv",
            symmetric = FALSE
  ) +
  ylab("") +
  xlab("months of the year") + theme(legend.position = "right") + scale_fill_brewer(palette = "Set2") + ggtitle("") + scale_y_log10()+ theme_minimal()

@@

ggpubr::annotate_figure(gg_fig,
                left = text_grob("electricity demand [KWh]",  rot = 90)) + theme_minimal()

@@

# plot for only customer is shown
# cust1 <- smart_meter10 %>%
# filter(customer_id %in% c(10006704)) %>%
#   prob_plot("wknd_wday",
#                             "hour_day",
#                             response = "general_supply_kwh",
#                             plot_type = "quantile",
#             symmetric = FALSE,
#             quantile_prob = c(0.25, 0.5, 0.75, 0.9))
#   scale_y_sqrt() +
#   ggtitle("Energy consumption distribution for customer id: 10006704")
cust2_quantile <- smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>%
  prob_plot("wknd_wday",
    "hour_day",
    response = "general_supply_kwh",
    plot_type = "quantile",
    symmetric = TRUE,
    quantile_prob = c(0.01, 0.1, 0.25, 0.5, 0.75, 0.9, 0.99)
  ) +
  scale_y_sqrt() +
  #ggtitle(" (b) Area quantile plot faceted by weekend-weekday") +
  ylab("electricity demand [KWh]") + xlab("hours of the day") + ggtitle("") + ylab("")+ 
  theme_minimal()
#
# smart_meter10 %>%
#   filter(customer_id %in% c(10006704)) %>%
#   prob_plot("wknd_wday",
#                             "hour_day",
#                             response = "general_supply_kwh",
#                             plot_type = "violin") +
#   scale_y_sqrt() +
#   ggtitle("Energy consumption distribution for customer id: 10006704")

cust2_violin <- smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>%
  prob_plot("wknd_wday",
    "hour_day",
    response = "general_supply_kwh",
    plot_type = "violin"
  ) +
  scale_y_sqrt()+
  #ggtitle(" (c) Violin plot faceted by weekend-weekday") +
  ylab("") + xlab("hours of the day") + ggtitle("") +
  scale_x_discrete( breaks = seq(0, 23, 5))+ 
  theme_minimal()

cust2_box <- smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>%
  prob_plot("hour_day",
    "wknd_wday",
    response = "general_supply_kwh",
    plot_type = "boxplot"
  ) +
  scale_y_sqrt() +
  #ggtitle(" (a) Box plot faceted by hour-of-day") +
  xlab("") +
  ggtitle("") + ylab("") +
  scale_x_discrete(labels = c('wday','wend')) +
  ggplot2::theme(axis.text.x = element_text(size = 7))+ 
  theme_minimal()

@@

First, it would be interesting to see if the distribution of total runs vary depending on if a team bats in the first or second inning. The Mumbai Indians (MI) and Chennai Super kings (CSK) <!--are considered one of the best teams in IPL with multiple winning titles and --> appeared in final playoffs from 2010 to 2015. We take their example in order to dive deeper into this question. <!--Circular granularities "over-of-inning" and "inning-of-match" can be computed using \ref{sec:circular-gran-def} with over as index of the tsibble.--> From Figure \ref{fig:cricex}(a), it can be observed that for the team batting in the first inning there is an upward trend of runs per over, while there is no clear upward trend in median and quartile deviation of runs for the teams batting in the second inning. This seem to indicate that players feel mounting presure to score more runs as they approach towards the end of the first inning. Whereas teams batting in the second inning have a set target in mind and are not subjected to such mounting press and may adopt a more conservative strategy, to score runs. Thus winning teams like CSK and MI seem to employ different inning strategies when it comes to their batting order.

@@

Another interesting question could be: do runs per over decrease in the subsequent over if fielding (defending) was good in the previous over? For establishing the fielding quality, we apply an indicator function on dismissals (1 if there was at least one wicket in the previous over due to run out or catch, 0 otherwise). Runs in the current over is then the observation variable.  <!--If a batsman is bowled out, it does not necessarily signify good fielding. So we only include number of catches and run out in an over as a measure of good fielding.
Difference in runs across overs are likely to be negative if good fielding has an impact on the runs scored in the subsequent overs. --> Dismissals in the previous over can lead to a batsman adopting a more defensive play style. Figure \ref{fig:cricex}(b) shows that no dismissals in the previous over leads to a higher median and quartile spread of runs per over as compared to the case when there has been at least one dismissal in the previous over.

@@

cricket_tsibble %>%
  filter(batting_team %in% c(
    "Mumbai Indians",
    "Chennai Super Kings"
  )) %>%
  mutate(inning = paste0("innings: ", inning)) %>%
  prob_plot("inning",
    "over",
    response = "runs_per_over",
    hierarchy_model,
    plot_type = "lv"
  ) +
  scale_fill_brewer(palette = "Dark2") +
  #ggtitle("(a) Runs per over across over faceted by inning") +
  theme(legend.position = "right") +
  ggtitle("a") +
  ylab("runs per over") +
  xlab("overs of the innings") +
  theme(plot.title = element_text(face = "bold")) +
  ggplot2::theme(
       strip.text = ggplot2::element_text(
        size = 10,
         margin = ggplot2::margin(b=0, t=0)
      )
     ) +  theme_minimal() 
#geom_smooth(aes( x = over,
#                               y=runs_per_over), method = lm, #formula = y ~ splines::bs(x, 3), se = FALSE)

@@

# filter(fielding_wckts %in% c(0,1)) %>%
#
 cricket_data %>%
  filter(over!=1) %>%
  prob_plot("over", "lag_field",
  hierarchy_model,
  response = "run_rate",
  plot_type = "boxplot",
  symmetric = FALSE,
 quantile_prob = c(0.25, 0.5, 0.75)) +
   #ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") +
  ylab("runs per over")  +
  xlab("number of wickets in previous over") +
  ggtitle("b") +
   theme(plot.title = element_text(face = "bold")) +  theme_minimal()
# + geom_boxplot(width = 0.5, aes(colour = lag_field))
```
